Leader functions and qualities across 59 cultures: an exploratory analysis

### 2019-12-02 leadership_across_cultures_contexts.Rmd
Modified cluster dendrograms. Minor edits to texts.

We analyzed data from our researcher-coded operationalized variables at the text-record level and at the culture-level. Our first goal was to assess the proportion of text records and cultures that provided evidence for each of our coded variables to discover the qualities, functions, benefits and costs of leadership that are most and least frequently noted in the ethnographic record. We computed confidence intervals for the proportion of text records supporting each variable using generalized linear mixed effects models and random intercepts based on document authors nested within cultures. We computed confidence intervals for the proportion of cultures with evidence for each variable using a cluster bootstrap.

@@

For each of the `r length(c(quality_vars, function_vars, leader_cost_vars, leader_benefit_vars, follower_benefit_vars, follower_cost_vars))` coded variables (see Tables \@ref(tab:qualfuncvars) and \@ref(tab:costbenefitvars) ), we computed the percentage of text records that provided support, estimating standard errors using a binomial generalized linear mixed effects model with a random intercept for author nested within culture (which partially accounts for potential variation due to differences in ethnographers such as gender, nationality, or philosophy). See Figure \@ref(fig:varsupport).

>>>>

We analyzed data from our researcher-coded operationalized variables at the text-record level and at the culture-level. Our first goal was to assess the proportion of text records and cultures that provided evidence for each of our coded variables to discover the qualities, functions, benefits and costs of leadership that are most and least frequently noted in the ethnographic record. We computed confidence intervals for the proportion of text records supporting each variable using generalized linear mixed effects models and random intercepts based on document authors nested within cultures (which partially accounts for potential variation due to differences in ethnographers such as gender, nationality, or theoretical framework). We computed confidence intervals for the proportion of cultures with evidence for each variable using a cluster bootstrap.

@@

For each of the `r length(c(quality_vars, function_vars, leader_cost_vars, leader_benefit_vars, follower_benefit_vars, follower_cost_vars))` coded variables (see Tables \@ref(tab:qualfuncvars) and \@ref(tab:costbenefitvars) ), we computed the percentage of text records that provided support, and we computed the percentage of cultures with at least one text record providing support for that variable. See Figure \@ref(fig:varsupport).
